\thesistitle

### 2019-06-12 sections/research.tex
Method call variability

\subsubsection{Referenced Types}
Many object-oriented programming languages (like Java, Python, C\#) require the programmer to import a type (or the class in which it is declared) before it can be used. Based on what is imported, the meaning of the name of a type can differ. For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java. However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT). Because of this, for type 1R clones, we compare the fully qualified identifier for all referenced types.

@@

Consider the example in figure \ref{fig:type2literal1}. In this example, the two methods have two literals that differ between them. We can perform an ``Extract method'' refactoring on these to get the result in figure \ref{fig:type2literal2}. In this process, we create a method parameter for the corresponding literal.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{img/type2literal1}
  \caption{Literal variability.}
  \label{fig:type2literal1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{img/type2literal2}
  \caption{Literal variability refactored.}
  \label{fig:type2literal2}
\end{figure}

\paragraph{Method call variability}

>>>>

\subsubsection{Referenced Types}
Many object-oriented programming languages (like Java, Python and C\#) require the programmer to import a type (or the class in which it is declared) before it can be used. Based on what is imported, the meaning of the name of a type can differ. For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java. However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT). Because of this, for type 1R clones, we compare the fully qualified identifier for all referenced types.

@@

Consider the example in figure \ref{fig:type2literal}. In this example, the two methods have two literals that differ between them. We can perform an ``Extract method'' refactoring on these to get the result that is displayed on the right. In this process, we create a method parameter for the corresponding literal.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/type2literal}
  \caption{Literal variability refactored.}
  \label{fig:type2literal}
\end{figure}

\paragraph{Method call variability}
Most modern programming languages (like Java, Python and C\#) allow to pass method references as a parameter to a method. This helps reducing duplication, as it is possible to refactor two code fragments which differ only by a method call. However, a method call does often not consist of a single token (like variables and literals). For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.

For type 2R clones, we allow called methods to vary as long as they have the same argument types and return type (both of them should be compared using their fully qualified identifiers). An example of this is shown in figure \ref{fig:type2method}. In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}). We use the ``Extract Method'' refactoring method to extract a new method and use a parameter for to pass the used method.

The method call variability property of type 2R clones imply that type 2R clones are not a subset of type 2 clones. Because methods calls can have a different structure, type 2R clones can be structurally slightly different. The example as shown in figure \ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used), but is not a type 2 clone.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/type2method}
  \caption{Method variability refactored.}
  \label{fig:type2method}
\end{figure}
